Different creatures in the R zoo

### 2024-07-06 text/22/r-creatures.Rmd
Updated 2022 Rmd files

---
title: "Different creatures in the R zoo"
author: "Steve Simon"
source: new
date: "2022-04-14"
category: 
- Blog post
tags:
- R software
output: html_document
---

@@

```{r}
secret_of_the_universe <- 42
on_first <- "Who"
y2k <- as.Date("2000-01-01")
```

@@

```{r}
buckle_my_shoe <- c(1, 2)
vowels <- c("A", "E", "I", "O", "U")
```

@@

```{r}
fantastic_four <- 1:4
fantastic_four
not_so_fantastic_four <- 5:8
not_so_fantastic_four
```

@@

```{r}
length(vowels)
```

@@

```{r}
vowels[1]
```

@@

```{r}
vowels[1:2]
vowels[c(2, 4)]
```

@@

```{r}
c(buckle_my_shoe, fantastic_four)
```

@@

```{r}
primes <- c(
  "first"=2,
  "second"=3,
  "third"=5,
  "fourth"=7)
primes
```

@@

```{r}
primes["first"]
primes[c("second", "fourth")]
```

@@

```{r}
names(primes)
```

@@

```{r}
mixed_vector <- c(1, "two")
mixed_vector
```

@@

```{r}
mixed_list <- list(1, "two")
mixed_list
```

@@

```{r}
mixed_list[[2]]
```

@@

```{r}
groceries <- list("bread", "fruit")
clothes <- list("socks", "underwear", "shirts")
shopping <- list(groceries, clothes)
shopping
```

@@

```{r}
unlist(shopping)
```

@@

```{r}
names(shopping) <- c("grocery_list", "clothing_list")
shopping <- list(grocery_list=groceries, clothing_list=clothes)
shopping
shopping[["clothing_list"]]
```

@@

```{r}
shopping$clothing_list
```

@@

```{r}
diagonal_matrix <- matrix(c(1, 0, 0, 0, 1, 0, 0, 0, 1), nrow=3)
diagonal_matrix
```

@@

```{r}
dim(diagonal_matrix)
```

@@

```{r}
diagonal_matrix[1, 3]
diagonal_matrix[1:2, 1:2]
```

@@

```{r}
diagonal_matrix[1, ]
diagonal_matrix[ , 3]
```

@@

```{r}
dimnames(diagonal_matrix) <- list(c("A", "B", "C"), c("D", "E", "F"))
diagonal_matrix
```

@@

```{r}
cbind(fantastic_four, not_so_fantastic_four)
rbind(fantastic_four, not_so_fantastic_four)
```

@@

```{r}
chain <- c(
  "Burger Queen",
  "McBurger",
  "Hardly's",
  "Out-n-In",
  "What? A Burger?",
  "Burger Bell",
  "Hedgehog")

@@

```{r}
fast_food_alt <- data.frame(fat, sodium, calories)
rownames(fast_food_alt) <- chain
fast_food_alt
```

@@

```{r}
fast_food[, 2]
fast_food[, "fat"]
fast_food$fat
```

@@

```{r}
library(tidyr)
fast_food_tibble <- tibble(chain, fat, sodium, calories)
```

@@

```{r}
library(survival)
tibble(colon)
```

@@

```{r}
print(tibble(colon), n=25)
```

@@

```{r}
fast_food[5, ]
fast_food_tibble[5, ]
fast_food[ , 2]
fast_food_tibble[ , 2]
fast_food[5, 2]
fast_food_tibble[5, 2]
```

@@

```{r}
real_fast_food <- fast_food[-4, ]
```

@@

```{r}
fast_food_regression <- lm(calories~fat+sodium, data=real_fast_food)
```

@@

```{r}
names(fast_food_regression)
```

@@

```{r}
fast_food_regression$coefficients
```

@@

```{r}
fast_food_regression$residuals
fast_food_regression$fitted.values
```

@@

```{r}
fast_food_regression$df.residual
```

@@

```{r}
fast_food_regression$qr
```

@@

```{r}
fast_food_summary <- summary(fast_food_regression)
names(fast_food_summary)
```

@@

```{r}
fast_food_summary$coefficients
```

@@

```{r}
fast_food_summary$coefficients[c("fat", "sodium"), "Pr(>|t|)"]
```

@@

```{r}
fast_food_summary$r.squared
fast_food_summary$adj.r.squared
```

@@

```{r}
fast_food_summary$fstatistic
```

>>>>

---
title: "Different creatures in the R zoo"
author: "Steve Simon"
source: new
date: "2022-04-14"
category: 
- Blog post
tags:
- R software
- Rmarkdown code
output: html_document
page_update: complete
---

@@

```{r r-creatures-01}
secret_of_the_universe <- 42
on_first <- "Who"
y2k <- as.Date("2000-01-01")
```

@@

```{r r-creatures-02}
buckle_my_shoe <- c(1, 2)
vowels <- c("A", "E", "I", "O", "U")
```

@@

```{r r-creatures-03}
fantastic_four <- 1:4
fantastic_four
not_so_fantastic_four <- 5:8
not_so_fantastic_four
```

@@

```{r r-creatures-04}
length(vowels)
```

@@

```{r r-creatures-05}
vowels[1]
```

@@

```{r r-creatures-06}
vowels[1:2]
vowels[c(2, 4)]
```

@@

```{r r-creatures-07}
c(buckle_my_shoe, fantastic_four)
```

@@

```{r r-creatures-08}
primes <- c(
  "first"=2,
  "second"=3,
  "third"=5,
  "fourth"=7)
primes
```

@@

```{r r-creatures-09}
primes["first"]
primes[c("second", "fourth")]
```

@@

```{r r-creatures-10}
names(primes)
```

@@

```{r r-creatures-11}
mixed_vector <- c(1, "two")
mixed_vector
```

@@

```{r r-creatures-12}
mixed_list <- list(1, "two")
mixed_list
```

@@

```{r r-creatures-13}
mixed_list[[2]]
```

@@

```{r r-creatures-14}
groceries <- list("bread", "fruit")
clothes <- list("socks", "underwear", "shirts")
shopping <- list(groceries, clothes)
shopping
```

@@

```{r r-creatures-15}
unlist(shopping)
```

@@

```{r r-creatures-16}
names(shopping) <- c("grocery_list", "clothing_list")
shopping <- list(grocery_list=groceries, clothing_list=clothes)
shopping
shopping[["clothing_list"]]
```

@@

```{r r-creatures-17}
shopping$clothing_list
```

@@

```{r r-creatures-18}
diagonal_matrix <- matrix(c(1, 0, 0, 0, 1, 0, 0, 0, 1), nrow=3)
diagonal_matrix
```

@@

```{r r-creatures-19}
dim(diagonal_matrix)
```

@@

```{r r-creatures-20}
diagonal_matrix[1, 3]
diagonal_matrix[1:2, 1:2]
```

@@

```{r r-creatures-21}
diagonal_matrix[1, ]
diagonal_matrix[ , 3]
```

@@

```{r r-creatures-22}
dimnames(diagonal_matrix) <- list(c("A", "B", "C"), c("D", "E", "F"))
diagonal_matrix
```

@@

```{r r-creatures-23}
cbind(fantastic_four, not_so_fantastic_four)
rbind(fantastic_four, not_so_fantastic_four)
```

@@

```{r r-creatures-24}
chain <- c(
  "Burger Queen",
  "McBurger",
  "Hardly's",
  "Out-n-In",
  "What? A Burger?",
  "Burger Bell",
  "Hedgehog")

@@

```{r r-creatures-25}
fast_food_alt <- data.frame(fat, sodium, calories)
rownames(fast_food_alt) <- chain
fast_food_alt
```

@@

```{r r-creatures-26}
fast_food[, 2]
fast_food[, "fat"]
fast_food$fat
```

@@

```{r r-creatures-27}
library(tidyr)
fast_food_tibble <- tibble(chain, fat, sodium, calories)
```

@@

```{r r-creatures-28}
library(survival)
tibble(colon)
```

@@

```{r r-creatures-29}
print(tibble(colon), n=25)
```

@@

```{r r-creatures-30}
fast_food[5, ]
fast_food_tibble[5, ]
fast_food[ , 2]
fast_food_tibble[ , 2]
fast_food[5, 2]
fast_food_tibble[5, 2]
```

@@

```{r r-creatures-31}
real_fast_food <- fast_food[-4, ]
```

@@

```{r r-creatures-32}
fast_food_regression <- lm(calories~fat+sodium, data=real_fast_food)
```

@@

```{r r-creatures-33}
names(fast_food_regression)
```

@@

```{r r-creatures-34}
fast_food_regression$coefficients
```

@@

```{r r-creatures-35}
fast_food_regression$residuals
fast_food_regression$fitted.values
```

@@

```{r r-creatures-36}
fast_food_regression$df.residual
```

@@

```{r r-creatures-37}
fast_food_regression$qr
```

@@

```{r r-creatures-38}
fast_food_summary <- summary(fast_food_regression)
names(fast_food_summary)
```

@@

```{r r-creatures-39}
fast_food_summary$coefficients
```

@@

```{r r-creatures-40}
fast_food_summary$coefficients[c("fat", "sodium"), "Pr(>|t|)"]
```

@@

```{r r-creatures-41}
fast_food_summary$r.squared
fast_food_summary$adj.r.squared
```

@@

```{r r-creatures-42}
fast_food_summary$fstatistic
```
